Pesticides in small agricultural streams in Germany

### 2016-08-12 article.tex
restructured figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticides pollution of small streams in Germany}
\abbreviations{mo, pest, ger, tu}
\keywords{Monitoring, Neonicotinoid, Germany, Toxic Units, Freshwater}

@@

Some journals require a graphical entry for the Table of Contents.
This should be laid out ``print ready'' so that the sizing of the
text is correct.

Inside the \texttt{tocentry} environment, the font used is Helvetica
8\,pt, as required by \emph{Journal of the American Chemical
Society}.

The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
permitted for  \emph{Journal of the American Chemical Society}
graphical table of content entries. The box will not resize if the
content is too big: instead it will overflow the edge of the box.

This box and the associated title will always be printed on a
separate page at the end of the document.

@@

\begin{figure}
  \includegraphics[width=.7\textwidth]{fig/fig1.pdf}
  \caption{Spatial distribution of the 3109 sampling sites. Colour codes different federal states.}
  \label{fig:fig1}
\end{figure}

In total 484 different compounds used as pesticides and their metobalites were measured at least once (Supplement, Table \todo{Set ref to table}). 
Most of the compounds were herbicides (179), followed by insecticides (117) and fungicides (109).
We found substantial differences of the spectra of analysed compounds between federal states (Figure \ref{fig:figvar}).
Hierarchical clustering revealed three groups:
i) with less then 100 compounds (SL, ST and TH), \\
ii) with a medium sized spectra and \\
iii) with a big and distinct spectra (RP and NI).

@@

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure xxx).}
  \label{fig:figvar}
\end{figure}

We were able to derive for 2376 sites catchment sizes and the proportion of agriculture within catchments. 
The distribution of sampling sites across catchment area and agricultural area in the catchment revealed a sharp decline in the distribution of catchment-sizes below $10~km^2$, with most sampling sites with catchments between 10 and 25 $km^2$ (Figure \ref{fig:figezglu}).
The proportion of agriculture in the catchments decreased with increasing catchment size.

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/ezglu.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points.
  }
  \label{fig:figezglu}
\end{figure}

@@

Modeling the number of RAC exceedances as function of agriculture within catchment and catchment size revealed that there is a strong and statistically significant increase up to 25\% agriculture.
Above this threshold the exceedances level off followed by a increase above 75\% (Figure \ref{fig:figrac}, left).

We could no detect any effect of catchment size on the number of RAC exceedances (Figure \ref{fig:figrac}, right) and no interaction between these two predictors.

\begin{figure}[h]
  \includegraphics[width=0.8\textwidth]{fig/figrac.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant changes. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:figrac}
\end{figure}

@@

\subsection{Pesticide pollution of small agricultural streams in germany}
Based on the results previous results and given the low amount of sample sites with catchment sizes below 10 km\textsuperscript{2} we explored the pollution of small agricultural streams, defined as streams with catchment size less than 30 km\textsuperscript{2} and more than 25\% agriculture within the catchment (n = 1030 sites with 10591 samples and 36550 measurements).
%EQS
Out of the 29 compounds with EQS, the most frequent EQS exceedances were recorded for the herbicides Nicosulfuron (2.1\%, n = 1769), Flufenacet (1.1\%, n = 6301) and Isoproturon (0.7\%, n = 8380). 
Other compounds show exceedances only at less then 0.5\% of all samples (Figure \ref{fig:figpol}A).
% RAC
Insecticides showed most exceedances of RAC. 
For Thiacloprid, Imidacloprid and Chlorpyrifos the RAC was less than LOQ, therefore, all detections have a RQ \textgreater 1 (Figure \ref{fig:figpol}B). 
Highest RQ was observed for Chlorpyrifos (244), Dimoxystrobin(117) and Isoproturon (80). 
% TU
In 33\% of the samples no compounds no compounds were detected. 
The mean $log(TU_{max})$ for detects was -4.6.
2.6\% of the samples showed $log(TU_{max})$ values greater then -2 (Figure \ref{fig:figpol}C).
%Mixtures
In most samples (55.5\%) more then one compound was detected, with a maximum of 54 different compounds (Figure \ref{fig:figpol}D).

\begin{figure}[h]
  \includegraphics[width=0.95\textwidth]{fig/pall.pdf}
  \caption{Overview on pesticide pollution of small agricultural streams. 
  A: 10 compounds with most frequent EQS exceedances. See B for color legend.
  B: 15 compounds with highest risk quotients.
  C: Distribution of $TU_{max}$ values. Values with $TU_{max} = 0$ are not displayed (3501 out of 10591 samples).
  D: Distribution of the number of detected compounds in a sample.
  }
  \label{fig:figpol}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Pesticides small streams]{Pesticides in small agricultural streams in Germany}
\abbreviations{mo, pest, ger, tu}
\keywords{Monitoring, Neonicotinoid, Germany, Toxic Units, Freshwater}
% RAC,

@@

\includegraphics[width=0.7\textwidth]{abstract.pdf}

@@

\begin{figure}[ht]
  \includegraphics[width=0.6\textwidth]{figure1.pdf}
  \caption{Spatial distribution of the 3109 sampling sites. Colour codes different federal states.}
  \label{fig:fig1}
\end{figure}

In total 484 different compounds used as pesticides and their metobalites were measured at least once (Supplement, Table \todo{Set ref to table}). 
Most of the compounds were herbicides (179), followed by insecticides (117) and fungicides (109).
We found substantial differences of the spectra of analysed compounds between federal states (Figure \ref{fig:fig2}).
Hierarchical clustering revealed three groups:
i) with less then 100 compounds (SL, ST and TH), \\
ii) with a medium sized spectra and \\
iii) with a big and distinct spectra (RP and NI).

@@

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure2.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure xxx).}
  \label{fig:fig2}
\end{figure}

We were able to derive for 2376 sites catchment sizes and the proportion of agriculture within catchments. 
The distribution of sampling sites across catchment area and agricultural area in the catchment revealed a sharp decline in the distribution of catchment-sizes below $10~km^2$, with most sampling sites with catchments between 10 and 25 $km^2$ (Figure \ref{fig:fig3}).
The proportion of agriculture in the catchments decreased with increasing catchment size.

\begin{figure}[ht]
  \includegraphics[width=.8\textwidth]{figure3.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points.
  }
  \label{fig:fig3}
\end{figure}

@@

Modeling the number of RAC exceedances as function of agriculture within catchment and catchment size revealed that there is a strong and statistically significant increase up to 25\% agriculture.
Above this threshold the exceedances level off followed by a increase above 75\% (Figure \ref{fig:fig4}, left).

We could no detect any effect of catchment size on the number of RAC exceedances (Figure \ref{fig:fig4}, right) and no interaction between these two predictors.

\begin{figure}[ht]
  \includegraphics[width=0.95\textwidth]{figure4.pdf}
  \caption{Effect of agriculture within the catchment (left) and catchment size (right) on the number of RAC exceedances. Red line marks statistically significant changes. Dashed lines denote 95\% Confidence Intervals.
  }
  \label{fig:fig4}
\end{figure}

@@

\subsection{Pesticide pollution of small agricultural streams in germany}
Based on the results previous results and given the low amount of sample sites with catchment sizes below 10 km\textsuperscript{2} we explored the pollution of small agricultural streams, defined as streams with catchment size less than 30 km\textsuperscript{2} and more than 25\% agriculture within the catchment (n = 1030 sites with 10591 samples and 36550 measurements).
%EQS
Out of the 29 compounds with EQS, the most frequent EQS exceedances were recorded for the herbicides Nicosulfuron (2.1\%, n = 1769), Flufenacet (1.1\%, n = 6301) and Isoproturon (0.7\%, n = 8380). 
Other compounds show exceedances only at less then 0.5\% of all samples (Figure \ref{fig:fig5}A).
% RAC
Insecticides showed most exceedances of RAC. 
For Thiacloprid, Imidacloprid and Chlorpyrifos the RAC was less than LOQ, therefore, all detections have a RQ \textgreater 1 (Figure \ref{fig:fig5}B). 
Highest RQ was observed for Chlorpyrifos (244), Dimoxystrobin(117) and Isoproturon (80). 
% TU
In 33\% of the samples no compounds no compounds were detected. 
The mean $log(TU_{max})$ for detects was -4.6.
2.6\% of the samples showed $log(TU_{max})$ values greater then -2 (Figure \ref{fig:fig5}C).
%Mixtures
In most samples (55.5\%) more then one compound was detected, with a maximum of 54 different compounds (Figure \ref{fig:fig5}D).

\begin{figure}[ht]
  \includegraphics[width=0.95\textwidth]{figure5.pdf}
  \caption{Overview on pesticide pollution of small agricultural streams. 
  \textbf{A}: 10 compounds with most frequent EQS exceedances. See B for color legend.
  \textbf{B}: Distribution of $TU_{max}$ values. Values with $TU_{max} = 0$ are not displayed (3501 out of 10591 samples).
  \textbf{C}: 15 compounds with highest risk quotients.
  \textbf{D}: Distribution of the number of detected compounds in a sample.
  }
  \label{fig:fig5}
\end{figure}
